Brownian Dynein Model

### 2015-09-12 latex/derivation.tex
Change naming scheme from left and right to bound and free. Add 'natural' mode to simulate.py.

\section{Cartesian from Angular Coordinates}
This section lays out the definitions of the coordinates of the Dynein model. \\
\begin{align}
  X_{bl} &= 0 \\
  X_{ml} &= X_{bl}+L_{s}\cos(\Theta_{bl}) \\
  X_{t}  &= X_{ml}+L_{t}\cos(\Theta_{ml}) \\
  X_{mr} &= X_{t} - L_{t}\cos(\Theta_{mr}) \\
  X_{br} &= X_{mr} - L_{s}\cos(\Theta_{br})
\end{align}

\begin{align}
  Y_{bl} &= 0 \\
  Y_{ml} &= Y_{bl}+L_{s}\sin(\Theta_{bl}) \\
  Y_{t}  &= Y_{ml}+L_{t}\sin(\Theta_{ml}) \\
  Y_{mr} &= Y_{t} +L_{t}\sin(\Theta_{mr}-\pi) = Y_{t} - L_{t}\sin(\Theta_{mr}) \\
  Y_{br} &= Y_{mr}+L_{s}\sin(\Theta_{br}-\pi) = Y_{mr} - L_{s}\sin(\Theta_{br})
\end{align}

\section{Cartesian Velocities}
This section shows the velocity definitions. \\
\begin{align}
  \dot{X}_{bl} &= 0 \\
  \dot{X}_{ml} &= \dot{X}_{bl} - L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} \\
  \dot{X}_{t } &= \dot{X}_{ml} - L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} \\
  \dot{X}_{mr} &= \dot{X}_{t } + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} \\
  \dot{X}_{br} &= \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br}
\end{align}

\begin{align}                                                                          
  \dot{Y}_{bl} &= 0 \\                                                        
  \dot{Y}_{ml} &= \dot{Y}_{bl} + L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} \\
  \dot{Y}_{t}  &= \dot{Y}_{ml} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} \\
  \dot{Y}_{mr} &= \dot{Y}_{t } - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} \\
  \dot{Y}_{br} &= \dot{Y}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}
\end{align}

\section{Cartesian Velocities (expanded)}
This section expands the above definitions. \\
\begin{align}
  \dot{X}_{bl} &= 0 \\
  \dot{X}_{ml} &= - L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} \\
  \dot{X}_{t } &= - L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} \\
  \dot{X}_{mr} &= - L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} \\
  \dot{X}_{br} &= - L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} - L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br}
\end{align}

\begin{align}                                                                               
  \dot{Y}_{bl} &= 0 \\                                                               
  \dot{Y}_{ml} &= L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} \\
  \dot{Y}_{t}  &= L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} \\
  \dot{Y}_{mr} &= L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} \\
  \dot{Y}_{br} &= L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} - L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} - L_{s}\cos(\Theta_{br})\dot{\Theta}_{br}
\end{align}

\section{Brownian Equations}
This section shows the velocity definitions using the Brownian dynamics equation. \\
\begin{align}  
  \dot{X}_{bl} &= 0 \\
  \dot{X}_{ml} &= \frac{1}{\gamma} \Big(F_{xml} + \mn \lambda_{ls}(X_{ml} - X_{bl}) + \lambda_{lt}(X_{t } - X_{ml}) \Big) + R_{xml} \\
  \dot{X}_{t } &= \frac{1}{\gamma} \Big(F_{xt } + \mn \lambda_{lt}(X_{t } - X_{ml}) + \lambda_{rt}(X_{mr} - X_{t }) \Big) + R_{xt } \\
  \dot{X}_{mr} &= \frac{1}{\gamma} \Big(F_{xmr} + \mn \lambda_{rt}(X_{mr} - X_{t }) + \lambda_{rs}(X_{br} - X_{mr}) \Big) + R_{xmr} \\
  \dot{X}_{br} &= \frac{1}{\gamma} \Big(F_{xbr} + \mn \lambda_{rs}(X_{br} - X_{mr})                                 \Big) + R_{xbr}
\end{align}

\begin{align}  
  \dot{Y}_{bl} &= 0 \\
  \dot{Y}_{ml} &= \frac{1}{\gamma} \Big(F_{yml} + \mn \lambda_{ls}(Y_{ml} - Y_{bl}) + \lambda_{lt}(Y_{t } - Y_{ml}) \Big) + R_{yml} \\
  \dot{Y}_{t}  &= \frac{1}{\gamma} \Big(F_{yt } + \mn \lambda_{lt}(Y_{t } - Y_{ml}) + \lambda_{rt}(Y_{mr} - Y_{t }) \Big) + R_{yt } \\
  \dot{Y}_{mr} &= \frac{1}{\gamma} \Big(F_{ymr} + \mn \lambda_{rt}(Y_{mr} - Y_{t }) + \lambda_{rs}(Y_{br} - Y_{mr}) \Big) + R_{ymr} \\
  \dot{Y}_{br} &= \frac{1}{\gamma} \Big(F_{ybr} + \mn \lambda_{rs}(Y_{br} - Y_{mr})                                 \Big) + R_{ybr}
\end{align}

@@

\begin{align}
  &L_{s}\sin(\Theta_{bl})  \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + R_{xml} \\
  &L_{s}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{t}\sin(\Theta_{ml})      \dot{\Theta}_{ml} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + \frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + R_{xt } \\
  &L_{s}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{t}\sin(\Theta_{ml})      \dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xmr} \\
  &L_{s}\sin(\Theta_{bl})  \dot{\Theta}_{bl} + L_{t}\sin(\Theta_{ml})      \dot{\Theta}_{ml} + L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} + L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xbr}
\end{align}

\begin{align}
  &\mn L_{s}\cos(\Theta_{bl})  \dot{\Theta}_{bl} = \frac{1}{\gamma}F_{yml} + \mn \frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + R_{yml} \\
  &\mn L_{s}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{t}\cos(\Theta_{ml})  \dot{\Theta}_{ml}  = \frac{1}{\gamma}F_{yt } + \mn \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + R_{yt } \\
  &\mn L_{s}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{t}\cos(\Theta_{ml})  \dot{\Theta}_{ml} + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} = \frac{1}{\gamma}F_{ymr} + \mn \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ymr} \\
  &\mn L_{s}\cos(\Theta_{bl})  \dot{\Theta}_{bl} + \mn L_{t}\cos(\Theta_{ml})  \dot{\Theta}_{ml} + \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} + \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} = \frac{1}{\gamma}F_{ybr} + \mn \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ybr}
\end{align}

@@

\begin{align}
  L_{s}\sin(\Theta_{bl})      \dot{\Theta}_{bl} &= \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + R_{xml} \\
  L_{t}\sin(\Theta_{ml})      \dot{\Theta}_{ml} &= \frac{1}{\gamma}F_{xt } - \frac{2}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + \frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + R_{xt } - \frac{1}{\gamma}F_{xml} - \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) - R_{xml} \\
  L_{t}\sin(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} &= \frac{1}{\gamma}F_{xmr} - \frac{2}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xmr} - \frac{1}{\gamma}F_{xt } - \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) - R_{xt } \\
  L_{s}\sin(\Theta_{br}-\pi)  \dot{\Theta}_{br} &= \frac{1}{\gamma}F_{xbr} - \frac{2}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xbr} - \frac{1}{\gamma}F_{xmr} - \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) - R_{xmr} 
\end{align}

\begin{align}
  \mn L_{s}\cos(\Theta_{bl})      \dot{\Theta}_{bl} &= \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + R_{yml} \\
  \mn L_{t}\cos(\Theta_{ml})      \dot{\Theta}_{ml} &= \frac{1}{\gamma}F_{yt } - \frac{2}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + R_{yt } - \frac{1}{\gamma}F_{yml} - \mn \frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) - R_{yml}\\
  \mn L_{t}\cos(\Theta_{mr}-\pi)  \dot{\Theta}_{mr} &= \frac{1}{\gamma}F_{ymr} - \frac{2}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ymr} - \frac{1}{\gamma}F_{yt } - \mn \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) - R_{yt } \\
  \mn L_{s}\cos(\Theta_{br}-\pi)  \dot{\Theta}_{br} &= \frac{1}{\gamma}F_{ybr} - \frac{2}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ybr} - \frac{1}{\gamma}F_{ymr} - \mn \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) - R_{ymr} 
\end{align}
\end{comment}

@@

\begin{align}  
  \dot{X}_{ml} &= \dot{X}_{bl} + \mn L_{s}\sin(\Theta_{bl})\dot{\Theta}_{bl} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{ls}(X_{ml} - X_{bl}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + R_{xml} \\
  \dot{X}_{t}  &= \dot{X}_{ml} + \mn L_{t}\sin(\Theta_{ml})\dot{\Theta}_{ml} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{ml}) + \frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + R_{xt } \\
  \dot{X}_{mr} &= \dot{X}_{t } + L_{t}\sin(\Theta_{mr})\dot{\Theta}_{mr} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{rt}(X_{mr} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xmr} \\
  \dot{X}_{br} &= \dot{X}_{mr} + L_{s}\sin(\Theta_{br})\dot{\Theta}_{br} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{rs}(X_{br} - X_{mr}) + R_{xbr}
\end{align}

\begin{align}  
  \dot{Y}_{ml} &= \dot{Y}_{bl} + L_{s}\cos(\Theta_{bl})\dot{\Theta}_{bl} = \frac{1}{\gamma}F_{yml} + \mn\frac{1}{\gamma}\lambda_{ls}(Y_{ml} - Y_{bl}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + R_{yml} \\
  \dot{Y}_{t}  &= \dot{Y}_{ml} + L_{t}\cos(\Theta_{ml})\dot{\Theta}_{ml} = \frac{1}{\gamma}F_{yt } + \mn\frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{ml}) + \frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + R_{yt } \\
  \dot{Y}_{mr} &= \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{mr})\dot{\Theta}_{mr} = \frac{1}{\gamma}F_{ymr} + \mn\frac{1}{\gamma}\lambda_{rt}(Y_{mr} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ymr} \\
  \dot{Y}_{br} &= \dot{Y}_{mr} + \mn L_{s}\cos(\Theta_{br})\dot{\Theta}_{br} = \frac{1}{\gamma}F_{ybr} + \mn\frac{1}{\gamma}\lambda_{rs}(Y_{br} - Y_{mr}) + R_{ybr}
\end{align}

@@

\subsection{Solving for $A_1$, $A_2$, $A_3$, $A_4$ and $X_1$}
In this section we take Equations (\ref{eq:Ax}) and (\ref{eq:Ay}), equate them and manipulate them to be in form $A_1\dot{\Theta}_{bl} + A_2 \dot{\Theta}_{ml} + A_3 \dot{\Theta}_{mr} + A_4 \dot{\Theta}_{br} = X_1$\\

@@

\begin{align}
\dot{\Theta}_{bl} &= \frac{N_{bl}}{D} \\
\dot{\Theta}_{ml} &= \frac{N_{ml}}{D} \\
\dot{\Theta}_{mr} &= \frac{N_{mr}}{D} \\
\dot{\Theta}_{br} &= \frac{N_{br}}{D}
\end{align}

>>>>

\section{Cartesian from Angular Coordinates}
This section lays out the definitions of the coordinates of the Dynein model. \\
\begin{align}
  X_{bb} &= 0 \\
  X_{bm} &= X_{bb}+L_{s}\cos(\Theta_{bb}) \\
  X_{t}  &= X_{bm}+L_{t}\cos(\Theta_{bm}) \\
  X_{fm} &= X_{t} - L_{t}\cos(\Theta_{fm}) \\
  X_{fb} &= X_{fm} - L_{s}\cos(\Theta_{fb})
\end{align}

\begin{align}
  Y_{bb} &= 0 \\
  Y_{bm} &= Y_{bb}+L_{s}\sin(\Theta_{bb}) \\
  Y_{t}  &= Y_{bm}+L_{t}\sin(\Theta_{bm}) \\
  Y_{fm} &= Y_{t} - L_{t}\sin(\Theta_{fm}) \\
  Y_{fb} &= Y_{fm} - L_{s}\sin(\Theta_{fb})
\end{align}

\section{Cartesian Velocities}
This section shows the velocity definitions. \\
\begin{align}
  \dot{X}_{bb} &= 0 \\
  \dot{X}_{bm} &= \dot{X}_{bb} - L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} \\
  \dot{X}_{t } &= \dot{X}_{bm} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} \\
  \dot{X}_{fm} &= \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} \\
  \dot{X}_{fb} &= \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb}
\end{align}

\begin{align}                                                                          
  \dot{Y}_{bb} &= 0 \\                                                        
  \dot{Y}_{bm} &= \dot{Y}_{bb} + L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} \\
  \dot{Y}_{t}  &= \dot{Y}_{bm} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} \\
  \dot{Y}_{fm} &= \dot{Y}_{t } - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} \\
  \dot{Y}_{fb} &= \dot{Y}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}
\end{align}

\section{Cartesian Velocities (expanded)}
This section expands the above definitions. \\
\begin{align}
  \dot{X}_{bb} &= 0 \\
  \dot{X}_{bm} &= - L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} \\
  \dot{X}_{t } &= - L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} \\
  \dot{X}_{fm} &= - L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} \\
  \dot{X}_{fb} &= - L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb}
\end{align}

\begin{align}                                                                               
  \dot{Y}_{bb} &= 0 \\                                                               
  \dot{Y}_{bm} &= L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} \\
  \dot{Y}_{t}  &= L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} \\
  \dot{Y}_{fm} &= L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} \\
  \dot{Y}_{fb} &= L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}
\end{align}

\section{Brownian Equations}
This section shows the velocity definitions using the Brownian dynamics equation. \\
\begin{align}  
  \dot{X}_{bb} &= 0 \\
  \dot{X}_{bm} &= \frac{1}{\gamma} \Big(F_{xml} + \mn \lambda_{ls}(X_{bm} - X_{bb}) + \lambda_{lt}(X_{t } - X_{bm}) \Big) + R_{xml} \\
  \dot{X}_{t } &= \frac{1}{\gamma} \Big(F_{xt } + \mn \lambda_{lt}(X_{t } - X_{bm}) + \lambda_{rt}(X_{fm} - X_{t }) \Big) + R_{xt } \\
  \dot{X}_{fm} &= \frac{1}{\gamma} \Big(F_{xmr} + \mn \lambda_{rt}(X_{fm} - X_{t }) + \lambda_{rs}(X_{fb} - X_{fm}) \Big) + R_{xmr} \\
  \dot{X}_{fb} &= \frac{1}{\gamma} \Big(F_{xbr} + \mn \lambda_{rs}(X_{fb} - X_{fm})                                 \Big) + R_{xbr}
\end{align}

\begin{align}  
  \dot{Y}_{bb} &= 0 \\
  \dot{Y}_{bm} &= \frac{1}{\gamma} \Big(F_{yml} + \mn \lambda_{ls}(Y_{bm} - Y_{bb}) + \lambda_{lt}(Y_{t } - Y_{bm}) \Big) + R_{yml} \\
  \dot{Y}_{t}  &= \frac{1}{\gamma} \Big(F_{yt } + \mn \lambda_{lt}(Y_{t } - Y_{bm}) + \lambda_{rt}(Y_{fm} - Y_{t }) \Big) + R_{yt } \\
  \dot{Y}_{fm} &= \frac{1}{\gamma} \Big(F_{ymr} + \mn \lambda_{rt}(Y_{fm} - Y_{t }) + \lambda_{rs}(Y_{fb} - Y_{fm}) \Big) + R_{ymr} \\
  \dot{Y}_{fb} &= \frac{1}{\gamma} \Big(F_{ybr} + \mn \lambda_{rs}(Y_{fb} - Y_{fm})                                 \Big) + R_{ybr}
\end{align}

@@

\begin{align}
  &L_{s}\sin(\Theta_{bb})  \dot{\Theta}_{bb} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{ls}(X_{bm} - X_{bb}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{bm}) + R_{xml} \\
  &L_{s}\sin(\Theta_{bb})  \dot{\Theta}_{bb} + L_{t}\sin(\Theta_{bm})      \dot{\Theta}_{bm} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{bm}) + \frac{1}{\gamma}\lambda_{rt}(X_{fm} - X_{t }) + R_{xt } \\
  &L_{s}\sin(\Theta_{bb})  \dot{\Theta}_{bb} + L_{t}\sin(\Theta_{bm})      \dot{\Theta}_{bm} + L_{t}\sin(\Theta_{fm}-\pi)  \dot{\Theta}_{fm} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{rt}(X_{fm} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{fb} - X_{fm}) + R_{xmr} \\
  &L_{s}\sin(\Theta_{bb})  \dot{\Theta}_{bb} + L_{t}\sin(\Theta_{bm})      \dot{\Theta}_{bm} + L_{t}\sin(\Theta_{fm}-\pi)  \dot{\Theta}_{fm} + L_{s}\sin(\Theta_{fb}-\pi)  \dot{\Theta}_{fb} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{rs}(X_{fb} - X_{fm}) + R_{xbr}
\end{align}

\begin{align}
  &\mn L_{s}\cos(\Theta_{bb})  \dot{\Theta}_{bb} = \frac{1}{\gamma}F_{yml} + \mn \frac{1}{\gamma}\lambda_{ls}(Y_{bm} - Y_{bb}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{bm}) + R_{yml} \\
  &\mn L_{s}\cos(\Theta_{bb})  \dot{\Theta}_{bb} + \mn L_{t}\cos(\Theta_{bm})  \dot{\Theta}_{bm}  = \frac{1}{\gamma}F_{yt } + \mn \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{bm}) + \frac{1}{\gamma}\lambda_{rt}(Y_{fm} - Y_{t }) + R_{yt } \\
  &\mn L_{s}\cos(\Theta_{bb})  \dot{\Theta}_{bb} + \mn L_{t}\cos(\Theta_{bm})  \dot{\Theta}_{bm} + \mn L_{t}\cos(\Theta_{fm}-\pi)  \dot{\Theta}_{fm} = \frac{1}{\gamma}F_{ymr} + \mn \frac{1}{\gamma}\lambda_{rt}(Y_{fm} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{fb} - Y_{fm}) + R_{ymr} \\
  &\mn L_{s}\cos(\Theta_{bb})  \dot{\Theta}_{bb} + \mn L_{t}\cos(\Theta_{bm})  \dot{\Theta}_{bm} + \mn L_{t}\cos(\Theta_{fm}-\pi)  \dot{\Theta}_{fm} + \mn L_{s}\cos(\Theta_{fb}-\pi)  \dot{\Theta}_{fb} = \frac{1}{\gamma}F_{ybr} + \mn \frac{1}{\gamma}\lambda_{rs}(Y_{fb} - Y_{fm}) + R_{ybr}
\end{align}

@@

\begin{align}
  L_{s}\sin(\Theta_{bb})      \dot{\Theta}_{bb} &= \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}\lambda_{ls}(X_{bm} - X_{bb}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{bm}) + R_{xml} \\
  L_{t}\sin(\Theta_{bm})      \dot{\Theta}_{bm} &= \frac{1}{\gamma}F_{xt } - \frac{2}{\gamma}\lambda_{lt}(X_{t } - X_{bm}) + \frac{1}{\gamma}\lambda_{rt}(X_{fm} - X_{t }) + R_{xt } - \frac{1}{\gamma}F_{xml} - \mn\frac{1}{\gamma}\lambda_{ls}(X_{bm} - X_{bb}) - R_{xml} \\
  L_{t}\sin(\Theta_{fm}-\pi)  \dot{\Theta}_{fm} &= \frac{1}{\gamma}F_{xmr} - \frac{2}{\gamma}\lambda_{rt}(X_{fm} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{fb} - X_{fm}) + R_{xmr} - \frac{1}{\gamma}F_{xt } - \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{bm}) - R_{xt } \\
  L_{s}\sin(\Theta_{fb}-\pi)  \dot{\Theta}_{fb} &= \frac{1}{\gamma}F_{xbr} - \frac{2}{\gamma}\lambda_{rs}(X_{fb} - X_{fm}) + R_{xbr} - \frac{1}{\gamma}F_{xmr} - \mn\frac{1}{\gamma}\lambda_{rt}(X_{fm} - X_{t }) - R_{xmr} 
\end{align}

\begin{align}
  \mn L_{s}\cos(\Theta_{bb})      \dot{\Theta}_{bb} &= \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}\lambda_{ls}(Y_{bm} - Y_{bb}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{bm}) + R_{yml} \\
  \mn L_{t}\cos(\Theta_{bm})      \dot{\Theta}_{bm} &= \frac{1}{\gamma}F_{yt } - \frac{2}{\gamma}\lambda_{lt}(Y_{t } - Y_{bm}) + \frac{1}{\gamma}\lambda_{rt}(Y_{fm} - Y_{t }) + R_{yt } - \frac{1}{\gamma}F_{yml} - \mn \frac{1}{\gamma}\lambda_{ls}(Y_{bm} - Y_{bb}) - R_{yml}\\
  \mn L_{t}\cos(\Theta_{fm}-\pi)  \dot{\Theta}_{fm} &= \frac{1}{\gamma}F_{ymr} - \frac{2}{\gamma}\lambda_{rt}(Y_{fm} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{fb} - Y_{fm}) + R_{ymr} - \frac{1}{\gamma}F_{yt } - \mn \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{bm}) - R_{yt } \\
  \mn L_{s}\cos(\Theta_{fb}-\pi)  \dot{\Theta}_{fb} &= \frac{1}{\gamma}F_{ybr} - \frac{2}{\gamma}\lambda_{rs}(Y_{fb} - Y_{fm}) + R_{ybr} - \frac{1}{\gamma}F_{ymr} - \mn \frac{1}{\gamma}\lambda_{rt}(Y_{fm} - Y_{t }) - R_{ymr} 
\end{align}
\end{comment}

@@

\begin{align}  
  \dot{X}_{bm} &= \dot{X}_{bb} + \mn L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} = \frac{1}{\gamma}F_{xml} + \mn\frac{1}{\gamma}\lambda_{ls}(X_{bm} - X_{bb}) + \frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{bm}) + R_{xml} \\
  \dot{X}_{t}  &= \dot{X}_{bm} + \mn L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} = \frac{1}{\gamma}F_{xt } + \mn\frac{1}{\gamma}\lambda_{lt}(X_{t } - X_{bm}) + \frac{1}{\gamma}\lambda_{rt}(X_{fm} - X_{t }) + R_{xt } \\
  \dot{X}_{fm} &= \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} = \frac{1}{\gamma}F_{xmr} + \mn\frac{1}{\gamma}\lambda_{rt}(X_{fm} - X_{t }) + \frac{1}{\gamma}\lambda_{rs}(X_{fb} - X_{fm}) + R_{xmr} \\
  \dot{X}_{fb} &= \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb} = \frac{1}{\gamma}F_{xbr} + \mn\frac{1}{\gamma}\lambda_{rs}(X_{fb} - X_{fm}) + R_{xbr}
\end{align}

\begin{align}  
  \dot{Y}_{bm} &= \dot{Y}_{bb} + L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} = \frac{1}{\gamma}F_{yml} + \mn\frac{1}{\gamma}\lambda_{ls}(Y_{bm} - Y_{bb}) + \frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{bm}) + R_{yml} \\
  \dot{Y}_{t}  &= \dot{Y}_{bm} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} = \frac{1}{\gamma}F_{yt } + \mn\frac{1}{\gamma}\lambda_{lt}(Y_{t } - Y_{bm}) + \frac{1}{\gamma}\lambda_{rt}(Y_{fm} - Y_{t }) + R_{yt } \\
  \dot{Y}_{fm} &= \dot{Y}_{t } + \mn L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} = \frac{1}{\gamma}F_{ymr} + \mn\frac{1}{\gamma}\lambda_{rt}(Y_{fm} - Y_{t }) + \frac{1}{\gamma}\lambda_{rs}(Y_{fb} - Y_{fm}) + R_{ymr} \\
  \dot{Y}_{fb} &= \dot{Y}_{fm} + \mn L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb} = \frac{1}{\gamma}F_{ybr} + \mn\frac{1}{\gamma}\lambda_{rs}(Y_{fb} - Y_{fm}) + R_{ybr}
\end{align}

@@

\subsection{Solving for $A_1$, $A_2$, $A_3$, $A_4$ and $X_1$}
In this section we take Equations (\ref{eq:Ax}) and (\ref{eq:Ay}), equate them and manipulate them to be in form $A_1\dot{\Theta}_{bb} + A_2 \dot{\Theta}_{bm} + A_3 \dot{\Theta}_{fm} + A_4 \dot{\Theta}_{fb} = X_1$\\

@@

\begin{align}
\dot{\Theta}_{bb} &= \frac{N_{bb}}{D} \\
\dot{\Theta}_{bm} &= \frac{N_{bm}}{D} \\
\dot{\Theta}_{fm} &= \frac{N_{fm}}{D} \\
\dot{\Theta}_{fb} &= \frac{N_{fb}}{D}
\end{align}
